Children's Books

### 2024-11-29 paper/paper.qmd
fixed pdf

---
title: "Children's Books"
subtitle: "What factors influence the likelihood of a book being high-rated"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format:
  pdf:
    fig.pos: "H"
toc: true
number-sections: true
bibliography: references.bib
---

@@

data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))
```

@@

# CONTINUTATION OF TABLE 1: CLEANED DATASET
# cant fit it in one line, put it next
second_half <- data %>% select(7:12)

@@

@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high-rated" had more pages on average than "low-rated books". Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2005 and 2003 for the "low-rated" and "high-rated" books respectively. "High-rated" books also received far more ratings on average at 8,000 ratings, more than four times that of "low-rated" books at an average of 2000 reviews per book. Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in @sec-data.

@@

@fig-most-common-covers shows the proportion of "high-rated" books for each cover type. `Kindle Edition` books had the highest proportions of "high-rated" books at 77.8%, followed by Paperback and Ebook, at 64.7% and 61.3% respectively. This illustrates that generally, digitally formatted books had higher proportions of "high-rated" books compared to physical formats. This finding also reflects the result from @tbl-summary-statistic.

@@

@fig-page-count shows that "high-rated" books have more page count than "low-rated" books. Highly-rated books had an average page count of 66.1, compared to the 57.6 average page count of low-rated books.

@@

@fig-publish-year shows the relationship between a book's rating and the publish year. The horizontal axis shows the publish year, and vertical axis shows the rating of the book. The graph is split into two vertically, the top plot showing ratings of high-rated books and low-rated books. It showed a left-tail distribution, peaking around the mid 2010s, followed by a big drop in late 2010s. High-rated books had a lower average publish year than low-rated books, at 2003 and 2005 respectively.

>>>>

---
title: "Children's Books"
subtitle: "What factors influence the likelihood of a book being high-rated?"
author: 
  - Hyunje Park
thanks: "Code and data are available at: [https://github.com/davidpxrk/childrens-book-rating](https://github.com/davidpxrk/childrens-book-rating). Special thanks to Rohan Alexander for his help!"
date: today
date-format: long
abstract: "This paper examines the factors influencing the rating of children's books using the data from Alex Cookson (Cookson 2020). By using a Bayesian logistic regression, I analyzed how various book characteristics impact the likelihood of a book receiving a high rating. The results showed that the book's cover type had the biggest positive impact on the likelihood of a book being high-rated. The insight from this research not only clarify the key elements of high-rated children's books, but also enhance future authors to push the boundaries of their literature by exploring different writing choices to enhance reader engagement."
format:
  pdf:
    fig.pos: "H"
toc: true
number-sections: true
bibliography: references.bib
---

@@

data <- read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

@@

# CONTINUTATION OF TABLE 1: CLEANED DATASET
# cant fit it in one line, put it next
second_half <- data %>% select(7:11)

@@

@tbl-summary-statistic shows a summary of detailed statistics about the cleaned dataset. It showed that books that were considered "high-rated" had more pages on average than "low-rated books". Furthermore, "high-rated" books were on average published 2 years before "low-rated" books, with publish year of 2002 and 2000 for the "low-rated" and "high-rated" books respectively. "High-rated" books also received far more ratings on average at 9,5092 ratings, more than four times that of "low-rated" books at an average of 2002 reviews per book. Lastly, `Kindle Edition` covers had the highest proportion of high-rated books out of any other cover types (as well as low-rated books). These variables are key in the analysis, and are further mentioned in @sec-data.

@@

@fig-most-common-covers shows the proportion of "high-rated" books for each cover type. `Kindle Edition` books had the highest proportions of "high-rated" books at 75%, followed by Paperback and Ebook, at 64% and 60.8% respectively. This illustrates that generally, digitally formatted books had higher proportions of "high-rated" books compared to physical formats. This finding also reflects the result from @tbl-summary-statistic.

@@

@fig-page-count shows that "high-rated" books have more page count than "low-rated" books. Highly-rated books had an average page count of 70.3, compared to the 66.9 average page count of low-rated books.

@@

@fig-publish-year shows the relationship between a book's rating and the publish year. The horizontal axis shows the publish year, and vertical axis shows the rating of the book. The graph is split into two vertically, the top plot showing ratings of high-rated books and low-rated books. It showed a left-tail distribution, peaking around the mid 2000s, followed by a big drop in late 2010s. High-rated books had a lower average publish year than low-rated books, at 2002 and 2000 respectively.
